---
title: "SCOPE forecast"
output:
  html_document: default
---
Here are the current conditions and 24-, 48-, and 72-hour forecasts for the area where SCOPE will be operating.  

### Current conditions
```{r, echo=FALSE}
rotate90 <- "style='transform:rotate(90deg);'"
```

```{r out.extra=rotate90, echo=FALSE}
sfc_map <- "https://tgftp.nws.noaa.gov/fax/PPBA11.gif"
knitr::include_graphics(sfc_map)
```

```{r, echo=FALSE}
sfc_seas <- "https://tgftp.nws.noaa.gov/fax/PJFB10.gif"
satellite <- "https://tgftp.nws.noaa.gov/fax/evpz11.jpg"
knitr::include_graphics(sfc_seas)
knitr::include_graphics(satellite)
```

### 24-hour forecast
```{r, echo=FALSE}
sfc_24hr <- "https://tgftp.nws.noaa.gov/fax/PYFE11.gif"
seas_24hr <- "https://tgftp.nws.noaa.gov/fax/PWFE11.gif"
knitr::include_graphics(sfc_24hr)
knitr::include_graphics(seas_24hr)
```

### 48-hour forecast
```{r, echo=FALSE}
sfc_48hr <- "https://tgftp.nws.noaa.gov/fax/PYFI11.gif"
seas_48hr <- "https://tgftp.nws.noaa.gov/fax/PJFI10.gif"
knitr::include_graphics(sfc_48hr)
knitr::include_graphics(seas_48hr)
```

### 72-hour forecast
```{r, echo=FALSE}
sfc_72hr <- "https://tgftp.nws.noaa.gov/fax/PYFK11.gif"
seas_72hr <- "https://tgftp.nws.noaa.gov/fax/PJFK10.gif"
knitr::include_graphics(sfc_72hr)
knitr::include_graphics(seas_72hr)
```

### References
You can find the full list of Pacific forecast product links at <https://www.weather.gov/media/marine/rfaxhi.txt> and
<https://www.weather.gov/marine/hawaiilatest> (different versions of the same info).  
  
A guide for map symbols is available at <https://www.nhc.noaa.gov/images/Graphical_Prod_Legend.jpg>.   
  
A detailed description of each of the maps is available at <https://ocean.weather.gov/UsersGuide/UGprint.php>.  
  
You can get an expanded package of maps at
<https://www.weather.gov/marine/hawaiibrief#>.  
